\subsection{Keywords}\label{sec:keywords}
These are the reserved keywords that have been used.  A convention has been introduced that defines all block-indicators to be denoted by an upper-case first character.

\begin{multicols}{4}
    \begin{enumerate}
        \item \texttt{repeat}\label{itm:repeat}
        \item \texttt{until}\label{itm:until}
        \item \texttt{or}\label{itm:or}
        \item \texttt{and}\label{itm:and}
        \item \texttt{forever}\label{itm:forever}
        \item \texttt{Create}\label{itm:Create}
        \item \texttt{Screen}\label{itm:Screen}
        \item \texttt{Entity}\label{itm:Entity}
        \item \texttt{MovePattern}\label{itm:MovePattern}
        \item \texttt{Exit}\label{itm:Exit}
        \item \texttt{ScreenExit}\label{itm:ScreenExit}
        \item \texttt{FloorExit}\label{itm:FloorExit}
        \item \texttt{Player}\label{itm:Player}
    \end{enumerate}
\end{multicols}

\ref{itm:repeat} indicates a loop. It is followed by \ref{itm:until} and expression, which can contain \ref{itm:or} or \ref{itm:and}. Otherwise, it is followed by \ref{itm:forever}, which indicates a never-ending loop.

\ref{itm:Create} is used to create a new instance. It is almost synonymous with \verb|new| in other languages.

\ref{itm:Screen} denotes a screen block, which is a container for other blocks like \verb|Map|, \verb|OnScreenEntered|, \verb|Entities|, and \verb|Exits|.

\ref{itm:Entity} is a block used to define what an entity is and what it does.

\ref{itm:MovePattern} is a block used to define a move pattern which can be applied to an entity.

\ref{itm:Exit}, \ref{itm:ScreenExit}, and \ref{itm:FloorExit} denotes exits or transitions to other screens. These are usually triggered by player movement.

\ref{itm:Player} is globally accessible and always points to the player. This allows the programmer to create interactions involving the player as well providing access to their properties such as health and move speed. 