\chapter{Difficulties in learning programming}


Due to higher demand for software developers in recent years, along with better pay than a lot of other industries (indsæt kilde), more people are looking to get into the field (kilde). 
To meet this demand websites such as udemy.com have been developed with the goal of teaching programming through interactive learning and video content in order to ease the barrier of entry into the field (kilde).  
Along with these, there also exists a number of websites such as CodeCombat.com that seek to teach programming through games to the younger generation. 

With the advent of these tools access to the industry has become much easier, but despite this, it is generally considered to be a long process to become proficient in software development (1). 
The difficulty arises from the fact that there are generally a lot of concepts that a novice developer has to grasp, while also having an understanding on when and how to apply these concepts. (1 & 2)

As explained by Robins & Rountree there are five areas in which a novice developer has to gain an understanding and mastery:

“(1) general orientation, what programs are for and what can be done with them; 
(2) the notional machine, a model of the computer as it relates to executing programs; 
(3) notation, the syntax and semantics of a particular programming language; 
(4) structures, that is, schemas/plans as discussed above; 
(5) pragmatics, that is, the skills of planning, developing, testing, debugging, and so on”
(2)

The struggle of learning these key points can be exemplified by the myriad of posts on community forums, such as reddit.com, where users can share their experiences and questions in regards to learning how to code.
In 2018, a user made a post on reddit.com called ”People who are struggling to learn to code, what's been the hardest part so far?”(4). 
In this post, users describe having had issues learning things ranging from loop structures to debugging, as well as having issues with the large amount of general information that has to be absorbed. 
While this information cannot be used as empirical evidence for difficulties in learning programming, it helps underline the fact that it is not a straight forward process. 




https://dl.acm.org/doi/pdf/10.1145/234867.234872 - Novice to expert
https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=7132770
https://www.tandfonline.com/doi/pdf/10.1076/csed.13.2.137.14200?needAccess=true
https://www.reddit.com/r/learnprogramming/comments/9j5lx1/people_who_are_struggling_to_learn_to_code_whats/
