\chapter{Learning} \label{chap:analysis}


There are various factors, ways and methods for how humans can learn something effectively. 
This section will focus on how developing a game, can be a good way for new programmers to start programming and a better way for them to learn it as well.\newline

One key factor in order to learn something effectively is through deliberate practice (deliberate practice). The term \emph{deliberate practice} is refered to as when an "individual intentionally repeats an activity in order to improve performance". 
This means in order for new programmers to effectively learn to code, it is not enough to simply view/listen to a tutorial on programming, nor is it enough to rotely repeat a given task over and over again. Instead it indcludes deliberate practice for the learning individual. This requires attention, rehearsal and repetition. 
In order to achieve these 3 things, one may look at the role of interest has, as this is also a very important thing for promoting effective learning. In a study on the importance of interest in education, interest can be defined as "both a psychological state of attention and affect toward a particular object or topic, and an enduring predisposition to reengage over time" (interest attention).
In other words, in order for new programmers to learn something effectively, it is first and foremost important that they practice deliberately. This requires attention, in which it is important for the new programmers to have an interest in what they are practicing. 
Secondly deliberate practice also required repetition. As mentioned in the above quote, interest plays an important role in this aspect as well, since interest can make it easier for programmers to repeatedly program more and more over time, while their attention and focus are being directed at the task at hand.\newline

In chapter... it can be seen that there are a lot of new programmers who gets into programming by developing/wanting to develop games. This means there is a big interest for game development and it is something more and more people want to get into. And as it was established in this section, interest plays an important role for promoting effective learning.
Game development can therefor be a very good way for people to learn progamming. 

// evt skrive at det er grunden til at vi valge vores målgruppe er nybegyndere...

\chapter{Video games and computer interest} \label{chap:analysis}
In this section the relationship between video games, interest in computer science and game development is discussed. \newline

Research from Georgia Institute of Technology has shown a positive correlation between playing video games and the interest in computer science. The research included a survey which 1116 students participated in; the results shows that 43\% of student claim that playing games have increased their interest in computing by a lot. 
Even though the results from the study show a low interest in becoming a computer scientist (6.9\%), nearly 10\% (92 out of 1116 students) reported that playing video games sparked a “desire to make games”. 
This means that a fair number of young students has the desire to make games without necessarily being interesting in learning or studying computer science. Therefore, a simple and easy programming language that enables the user to quickly create and explore the possibilities in game development could be in demand.
As discussed in the previous section interest plays an important role in effective learning. Therefore learning a simple code language could be a good stepping stone to help understand a more complex languages.

\chapter{How to get more people starting with programming}\label{chap:analysis}

This section will focus on how to get more people  to start programming and what the best way to teach it is. \newline

Learning how to code is not easy, taking the first steps into this huge universe might seem like a daunting, if not intimidating task. All software is written in some kind of coding language and every coding language is unique, designed with a certain operating system, platform, coding style and intended use in mind. 
That is why many have a hard time starting to program because the coding world can be complicated and confusing to get into. It takes years of pratice to learn everything necessary to get beyond just a basic level where you can write short programs that work. It takes hours of practice.
There are plenty of free resources beginners can use to give themselves all the help they need. It can help them teach new techniques, and make the learning process fun and exciting. 
One of the most important ways before starting to program, is to find a reason to learn a programmming language. The answer can help determine which programming language should be used whetever it is to make a new indie game or making the newest application.
Another way to get the best learning expericence is to get a real book that you can follow along from beginning till the end. This will give more comprehensive introduction to coding than jumping around from topic to topic on a website. Another idea to start programming is to watch educational videos about nearly any coding related topic. 
It will give a more understanding of the topic and can be helping guidelines to the personal project a person want to make. 



  
