\chapter{Problem Analysis} \label{chap:analysis}
Learning how to code is hard.
It is no wonder that the most viewed video on YouTube for the search term '\textit{learn programming}' has been viewed 23 million times\cite{LearnProgrammingYouTube}.
The video concerns itself with \textit{Python}, a language that is regarded as an easy to learn for beginners\cite{PythonBeginners}.

A common error, and source of frustration, for new programmers is syntax errors.
Other issues include types and confusing error outputs \cite{bosseWhyProgrammingDifficult2017}.
New programmers also have difficulties with the application of programming concepts.
This could be because learning isn't practical enough\cite{lahtinenStudyDifficultiesNovice2005}.
You have to program to learn how to program.

Is a simple language, like Python\cite{WhatPythonExecutive}, the solution for new programmers?
Research indicates that it might be. A simple language gives rise to fewer syntax errors as well as fewer logic errors.
Furthermore, learning a simpler language does not seem to hinder the learner when moving to a more complex language\cite{mannilaWhatSimpleLanguage2006}.


Knowing this, can a simple language be created which acts as a bridge to programming for beginners?
Before a more specific problem can be identified, we will get an overview of some existing solutions to this problem.

\include{sections/1_analysis/existing_solutions}
% !! On the background of the existing solutions, we can draw some conclusions and narrow the problem down...
\include{sections/1_analysis/initial_problem}
% !! Now that the initial problem has been specified, we can bridge towards design...
\include{sections/1_analysis/scientific_research}